A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-08-07 pilot-publication/lab-book.Rmd
Fix broken bootstrap caused by data entry error

>>>>

## Strange error when running bootstrap on real data

I get this strange error when I try to run the bootstrap on the real data:

```{r}
## Error in `add_column()`:
## ! New columns must be compatible with `.data`.
## ✖ New column has 112 rows.
## ℹ `.data` has 111 rows.
## Backtrace:
##     ▆
##  1. ├─boot::boot(data, estimate_outcome_results, R = n.boot.samples)
##  2. │ └─global statistic(data, original, ...)
##  3. │   └─outcomes.tables$absolute.difference %>% as_tibble() %>% ...
##  4. └─tibble::add_column(., outcomes.row.names, .before = 1)
##  5.   └─tibble:::abort_incompatible_new_cols(nrow(.data), df)
##  6.     └─tibble:::tibble_abort(...)
##  7.       └─rlang::abort(x, class, ..., call = call, parent = parent, use_cli_format = TRUE)
## Execution halted
```

The cause of the error is the entry 995 in the variable `complications__number_of_hospitalizations_for_this_injury`. Not sure where that entry comes from, but most likely it should be 999 but something went wrong? A quick fix is to replace this value with 999 in the `prepare_data` function, which should work.
